\documentclass{article}

\usepackage{neurips_2026}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{graphicx}

\title{Predicting Short-Term Stock Price Movements Using Machine Learning: A Comparative Study of Classical Classifiers with Technical Indicators}

\author{%
  Albert Kim \\
  Section ID: [8] \\
  NetID: ak2002 \\
  Rutgers University \\
  \texttt{ak2002@scarletmail.rutgers.edu} \\
  \And
  Alex Gonzalez \\
  Section ID: [5] \\
  NetID: ag2616 \\
  Rutgers University \\
  \texttt{Ag2616@scarletmail.rutgers.edu} \\
  \And
  Rithvik Kuchuru \\
  Section ID: [6] \\
  NetID: rrk88 \\
  Rutgers University \\
  \texttt{rrk88@scarletmail.rutgers.edu} \\
}

\begin{document}

\maketitle

\begin{abstract}
We present an empirical study of three classical machine learning classifiers ---
Logistic Regression, Random Forest, and Support Vector Machines (SVM) --- for
next-day binary price direction prediction on five large-cap U.S.\ equities
(AAPL, MSFT, GOOGL, AMZN, JPM) spanning 2018--2022 (approximately 6,150 total
observations). Using a strict chronological 80/20 train-test split with eight
engineered technical features, Random Forest achieves the strongest performance
with a mean test accuracy of 57.2\% and F1-score of 0.573; a feature ablation
study identifies the 5-day SMA ratio and rolling volatility as dominant
predictors. Generalization analysis confirms modest, well-controlled overfitting
across all models, providing empirical support for the semi-strong form of the
Efficient Market Hypothesis while demonstrating that non-linear ensemble methods
capture weak but consistent predictive signals that linear classifiers cannot.

\noindent Code: \url{https://github.com/allbertkim/Final-Project.git}.\newline
\noindent Video: \newline \url{https://drive.google.com/file/d/18zh1U028J-iT1AcShutagNW8r-Y29GlD/view?usp=sharing}.
\end{abstract}

% -----------------------------------------------------------------------
\section{Introduction}
% -----------------------------------------------------------------------

Predicting stock price movements remains a fundamentally challenging problem.
Algorithmic trading systems and individual investors who fail to account for
the inherent limits of predictive modeling risk significant financial losses:
even a 1\% systematic miscalibration in prediction confidence can translate to
substantial portfolio drawdowns when decisions are automated at scale. Despite
this practical urgency, the computer vision and NLP communities have received
considerably more attention than classical ML applied to financial time series,
and the relative merits of simple technical indicator-based approaches remain
under-characterized on modern data.

The Efficient Market Hypothesis (EMH) \citep{fama1970} posits that asset prices
fully reflect available information, implying that consistent prediction should
not be possible. Despite this, machine learning methods have shown potential in
extracting weak predictive signals from structured financial data
\citep{fischer2018}, particularly over short time horizons where price momentum
and volume signals carry transient information before being arbitraged away.

This study investigates whether classical machine learning models can predict
short-term stock price direction using technical indicators derived from
historical OHLCV data, and identifies \emph{which} features and model properties
drive whatever signal exists. Our contributions are:

\begin{itemize}
    \item We construct a fully reproducible machine learning pipeline for
    next-day stock price direction prediction using five years of daily OHLCV
    data across five large-cap equities, with strict chronological evaluation
    to prevent look-ahead bias.

    \item We conduct a controlled comparison of Logistic Regression, Random
    Forest, and SVM, establishing that Random Forest outperforms linear
    baselines by 2--4\% in F1-score due to non-linear feature interactions
    rather than memorization.

    \item We perform a \textbf{feature ablation study} to identify the
    contribution of each technical indicator individually, finding that short-
    term momentum (5-day SMA ratio) and rolling volatility are the dominant
    predictors.

    \item We analyze generalization gaps across all three models, confirming
    that tree-depth regularization effectively controls Random Forest
    overfitting while preserving its accuracy advantage on held-out data.

    \item We provide an honest quantitative assessment showing all models
    perform only modestly above the 50\% random baseline, providing empirical
    support for the semi-strong EMH on large-cap equities.
\end{itemize}

% -----------------------------------------------------------------------
\section{Related Work}
% -----------------------------------------------------------------------

\subsection{Efficient Market Hypothesis and Its Critiques}

\citet{fama1970} introduced the EMH, arguing that asset prices fully reflect
all available information. Under the semi-strong form, models relying only on
historical price data should achieve accuracy near chance. However, empirical
studies have documented short-lived momentum effects and volatility clustering
that suggest exploitable patterns exist over very short time horizons
\citep{fischer2018}. Our work directly tests this boundary on recent data.

\subsection{Classical Machine Learning for Financial Forecasting}

\citet{cortes1995} introduced Support Vector Machines, which have been widely
applied to financial time-series classification due to their strong
generalization in high-dimensional spaces. \citet{breiman2001} proposed Random
Forests, which mitigate overfitting through bagging and feature randomization
and have shown competitive performance on financial classification tasks.
Logistic Regression serves as an interpretable linear baseline, widely used in
the financial ML literature for its regulatory transparency.

\subsection{Technical Indicators as Predictive Features}

Technical analysis indicators --- including moving averages, RSI, and Bollinger
Bands --- have been used by practitioners to identify market trends
\citep{murphy1999}. \citet{fischer2018} validated the utility of momentum and
volatility features for supervised learning in short-term forecasting. Our work
extends this by conducting a systematic feature ablation to isolate which
indicators contribute most, rather than treating the feature set as a monolithic
input.

% -----------------------------------------------------------------------
\section{Method}
% -----------------------------------------------------------------------

We design a structured machine learning pipeline for binary stock price movement
prediction. The pipeline consists of four stages: data collection and
preprocessing, feature engineering, model training, and evaluation.

\subsection{Data Collection and Preprocessing}

We use historical daily OHLCV stock price data obtained from Yahoo Finance via
the \texttt{yfinance} Python library. The dataset covers five large-cap U.S.
equities (AAPL, MSFT, GOOGL, AMZN, JPM) over a five-year period (January
2018 -- December 2022), yielding approximately 1,250 daily observations per
stock after removing trading holidays.

The prediction target is a binary label $y_t \in \{0, 1\}$, where $y_t = 1$
indicates the closing price on day $t+1$ is strictly higher than on day $t$:
\[
y_t =
\begin{cases}
1 & \text{if } P_{t+1} > P_t \\
0 & \text{otherwise}
\end{cases}
\]
This formulation transforms the regression problem into a binary classification
task. The baseline accuracy of a majority-class predictor on this dataset is
approximately 50\%, since upward and downward days occur with roughly equal
frequency across the five stocks.

Preprocessing steps include: (1) \textbf{Missing value handling}: forward-fill
for gaps due to corporate actions or data provider errors; (2)
\textbf{Normalization}: min-max scaling applied to all numerical features to
ensure comparability across indicators, fitted on training data only to prevent
leakage; (3) \textbf{Train/test split}: a strict chronological 80/20 split is
used to prevent look-ahead bias. The most recent 20\% of observations form the
held-out test set.

\subsection{Feature Engineering}

Raw OHLCV data is augmented with eight technical indicators capturing short- and
medium-term momentum and volatility signals:

\begin{itemize}
    \item \textbf{Simple Moving Average (SMA)}: 5-day and 20-day windows to
    capture short- and medium-term price trends.
    \item \textbf{Daily Return}: Percentage change $r_t = (P_t - P_{t-1}) /
    P_{t-1}$, capturing first-order price momentum.
    \item \textbf{Rolling Volatility}: Standard deviation of daily returns over
    a 10-day window as a proxy for market uncertainty.
    \item \textbf{Volume Change}: Percentage change in trading volume, capturing
    shifts in market participation.
    \item \textbf{Price-to-SMA Ratio}: Ratio of closing price to the 20-day SMA,
    reflecting mean-reversion signals.
\end{itemize}

Rows corresponding to the warm-up period of the longest rolling window are
dropped, yielding approximately 1,230 usable samples per stock. All features
are computed using only past observations to prevent any form of data leakage.

\subsection{Models}

We implement and compare three classification models:

\textbf{Logistic Regression.} A linear baseline modeling log-odds of an upward
price movement as a linear combination of input features. Trained with L2
regularization ($C = 1.0$) using the \texttt{lbfgs} solver with a maximum of
1,000 iterations.

\textbf{Random Forest Classifier.} An ensemble of 100 decision trees
\citep{breiman2001}, each trained on a bootstrap sample with a random subset of
features at each split. We set \texttt{max\_depth=10} and
\texttt{min\_samples\_leaf=5} to control overfitting. Predictions are determined
by majority vote.

\textbf{Support Vector Machine (SVM).} A kernel-based classifier
\citep{cortes1995} using an RBF kernel with $C = 1.0$ and $\gamma =
\texttt{scale}$. Input features are standardized to zero-mean, unit-variance
prior to training.

\subsection{Loss Function and Optimization}

For Logistic Regression and SVM, optimization minimizes cross-entropy loss with
L2 regularization:
\[
\mathcal{L} = -\frac{1}{N}\sum_{i=1}^{N} \left[ y_i \log \hat{y}_i + (1-y_i)
\log(1-\hat{y}_i) \right] + \frac{\lambda}{2} \|\mathbf{w}\|^2
\]
where $\hat{y}_i$ is the predicted probability, $y_i$ is the ground-truth label,
and $\lambda$ controls regularization strength. Random Forest uses Gini impurity
as the splitting criterion.

\subsection{Reproducibility}

All experiments use fixed random seeds (\texttt{random\_state=42} for all
stochastic models). The full pipeline is strictly ordered to prevent any form
of data leakage:

\begin{enumerate}
    \item \textbf{Feature computation}: All technical indicators are computed
    using only past observations (no look-ahead). Rolling windows are anchored
    to day $t$ and look backward exclusively.
    \item \textbf{Warm-up removal}: Rows within the warm-up period of the
    longest rolling window (20 days) are dropped before splitting.
    \item \textbf{Chronological train/test split}: The first 80\% of
    observations (by date) form the training set; the final 20\% form the
    held-out test set. No shuffling is applied at any stage.
    \item \textbf{Normalization}: Min-max scaler is fit \emph{only} on
    training data and then applied to both training and test features.
    \item \textbf{Model training}: Models are fit on training features and
    labels only.
    \item \textbf{Evaluation}: All metrics are computed on the held-out test
    set. Training metrics are computed separately for generalization analysis
    only.
\end{enumerate}

This ordering ensures that no future information contaminates either feature
computation or normalization, which are two common sources of inadvertent
leakage in financial ML pipelines. The complete source code, including the
exact sequence of operations and random seeds, is available at the repository
linked in the abstract.

% -----------------------------------------------------------------------
\section{Evaluation}
% -----------------------------------------------------------------------

\subsection{Experimental Setup}

\textbf{Dataset and Partitioning.} We evaluate on five large-cap U.S. equities
spanning January 2018 to December 2022. Each stock contributes approximately
1,230 usable samples. The dataset is split chronologically into 80\% training
(approximately 984 samples) and 20\% testing (approximately 246 samples) per
stock to avoid look-ahead bias. No separate validation set is used; all
hyperparameters were fixed prior to final evaluation.

\textbf{Implementation Details.} All models are implemented in
\texttt{scikit-learn} (v1.3). Hyperparameters were selected based on domain
knowledge and preliminary cross-validation on the training set only.

\textbf{Hardware and Environment.} All experiments were conducted on a standard
personal computer with an Intel Core i7 CPU and 16 GB RAM, running Python 3.10
with \texttt{scikit-learn}, \texttt{pandas}, and \texttt{yfinance}. Total
training time across all models and stocks is under 5 minutes.

\subsection{Overall Model Performance}

We evaluate all three models using accuracy, precision, recall, and F1-score on
the held-out test set, averaged across all five stocks. Results are summarized
in Table~\ref{tab:results}.

\begin{table}[ht]
\centering
\caption{Classification performance on the test set (averaged across 5 stocks).
All values are averages over per-stock results. The 50\% random baseline is
included for reference.}
\label{tab:results}
\begin{tabular}{lcccc}
\toprule
\textbf{Model} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-Score} \\
\midrule
Random Baseline        & 0.500 & 0.500 & 0.500 & 0.500 \\
\midrule
Logistic Regression    & 0.531 & 0.528 & 0.541 & 0.534 \\
Support Vector Machine & 0.548 & 0.545 & 0.553 & 0.549 \\
Random Forest          & \textbf{0.572} & \textbf{0.569} & \textbf{0.578} & \textbf{0.573} \\
\bottomrule
\end{tabular}
\end{table}

Random Forest achieves the best performance across all metrics, with a mean test
accuracy of 57.2\% and F1-score of 0.573 --- a 7.2 percentage point improvement
over the random baseline. SVM follows at 54.8\%, while Logistic Regression
achieves 53.1\%, confirming that non-linear feature interactions provide
incremental but consistent gains.

\subsection{Feature Ablation Study}

To understand which features drive predictive performance, we conduct a leave-
one-out feature ablation on the Random Forest model. We retrain the model eight
times, each time removing a single feature, and measure the drop in test F1-
score relative to the full model (Table~\ref{tab:ablation}).

\begin{table}[ht]
\centering
\caption{Feature ablation results. Each row shows the test F1-score when the
corresponding feature is removed from the Random Forest model. A larger drop
indicates a more important feature.}
\label{tab:ablation}
\begin{tabular}{lcc}
\toprule
\textbf{Feature Removed} & \textbf{Test F1} & \textbf{Drop vs. Full (0.573)} \\
\midrule
None (Full Model)       & 0.573 & --- \\
5-day SMA Ratio         & 0.541 & $-$0.032 \\
Rolling Volatility      & 0.548 & $-$0.025 \\
Daily Return            & 0.558 & $-$0.015 \\
Volume Change           & 0.566 & $-$0.007 \\
20-day SMA              & 0.568 & $-$0.005 \\
5-day SMA               & 0.569 & $-$0.004 \\
Price-to-SMA Ratio      & 0.570 & $-$0.003 \\
\bottomrule
\end{tabular}
\end{table}

The 5-day SMA ratio and rolling volatility are the most critical features,
contributing drops of 0.032 and 0.025 in F1-score respectively when removed.
This confirms that short-term momentum and market uncertainty carry the most
predictive signal. Raw volume and longer-horizon indicators contribute
marginally, consistent with their role as slower-moving signals.

\subsection{Generalization Analysis}

We analyze the generalization gap (training accuracy minus test accuracy) for
each model to assess overfitting. Results are shown in Table~\ref{tab:gap}.

\begin{table}[ht]
\centering
\caption{Generalization gap analysis. A smaller gap indicates better
generalization to unseen data.}
\label{tab:gap}
\begin{tabular}{lccc}
\toprule
\textbf{Model} & \textbf{Train Acc.} & \textbf{Test Acc.} & \textbf{Gap} \\
\midrule
Logistic Regression    & 0.542 & 0.531 & 0.011 \\
Support Vector Machine & 0.578 & 0.548 & 0.030 \\
Random Forest          & 0.652 & 0.572 & 0.080 \\
\bottomrule
\end{tabular}
\end{table}

Random Forest shows the largest gap (0.08), indicating moderate overfitting that
is well-controlled by the \texttt{max\_depth} and \texttt{min\_samples\_leaf}
constraints. Linear models show smaller gaps (0.03 and 0.01) due to their lower
model capacity. Importantly, Random Forest maintains the highest test accuracy
despite its larger gap, confirming that its regularization prevents
memorization while preserving its non-linear advantage.

\subsection{Per-Stock Performance Breakdown}

Table~\ref{tab:perstockstock} presents Random Forest test accuracy broken down
by individual stock to assess consistency across assets.

\begin{table}[ht]
\centering
\caption{Random Forest test accuracy by individual stock.}
\label{tab:perstockstock}
\begin{tabular}{lccccc}
\toprule
\textbf{Metric} & \textbf{AAPL} & \textbf{MSFT} & \textbf{GOOGL} & \textbf{AMZN} & \textbf{JPM} \\
\midrule
Test Accuracy & 0.581 & 0.574 & 0.568 & 0.559 & 0.578 \\
F1-Score      & 0.583 & 0.571 & 0.565 & 0.556 & 0.590 \\
\bottomrule
\end{tabular}
\end{table}

Performance is consistent across all five stocks (range: 0.559--0.581), ruling
out that aggregate results are driven by a single favorable stock. JPM
(financial sector) achieves the highest F1-score (0.590), potentially reflecting
stronger momentum signals in financial sector equities compared to technology
stocks.

% -----------------------------------------------------------------------
\section{Discussion}
% -----------------------------------------------------------------------

\subsection{Interpreting Model Performance}

All three models achieve test accuracy modestly above the 50\% random baseline,
consistent with the semi-strong form of the EMH \citep{fama1970}. The Random
Forest advantage over linear models suggests that non-linear interactions
between technical indicators --- such as the joint effect of momentum and
volatility --- carry predictive signal that a linear classifier cannot capture.
The underperformance of Logistic Regression confirms that the relationship
between technical features and next-day price direction is not well approximated
by a linear decision boundary.

Notably, performance is consistent across all five stocks (Table~\ref{tab:perstockstock}),
ruling out that results are driven by a lucky subset. This consistency
strengthens confidence that the weak but positive signal is a real structural
property of these markets rather than statistical noise.

\textbf{Effect of the COVID-19 Regime.} The evaluation window (January 2018 --
December 2022) spans an exceptional market event: the COVID-19 crash and
recovery of March--May 2020. During this period, intraday and daily volatility
reached multi-decade highs, and momentum-based signals briefly became highly
predictive before markets stabilized. Because this event falls within our
training set (the first 80\% of each stock's chronological data), the Random
Forest may have learned patterns specific to high-volatility regimes that do not
generalize. This is consistent with the slightly elevated generalization gap
observed for Random Forest ($\Delta = 0.08$) compared to the linear models.
Future work should conduct a regime-stratified evaluation --- comparing
performance during the 2018--2019 pre-COVID period, the 2020 crash window, and
the 2021--2022 recovery --- to disentangle the contribution of volatility regime
from model capacity.

\textbf{Comparison to Chance by Model Complexity.} The monotonic relationship
between model complexity and test accuracy (Logistic Regression $<$ SVM $<$
Random Forest) is informative: it implies that each additional layer of
expressiveness recovers a small but consistent amount of signal from non-linear
feature interactions. However, the diminishing returns are notable --- the gap
between SVM and Random Forest (1.7\%) is smaller than between Logistic
Regression and SVM (1.7\%), suggesting that further increasing model complexity
(e.g., gradient boosting or deep learning) may yield only marginal gains without
additional features or data.

\subsection{Role of Feature Engineering}

The ablation study (Table~\ref{tab:ablation}) confirms that derived indicators
are substantially more predictive than raw data. The 5-day SMA ratio captures
the relationship between current price and recent trend, encoding
mean-reversion and breakout signals simultaneously. Rolling volatility reflects
market uncertainty, which appears to correlate with subsequent directional
moves.

The marginal contribution of raw volume and the 20-day SMA (drops of only
0.005--0.007 in F1 when removed) is consistent with their role as slower-moving
signals that are largely subsumed by the shorter-horizon indicators already in
the feature set. The 20-day SMA, for instance, is partly redundant with the
5-day SMA ratio, which already encodes how the current price relates to the
medium-term trend.

These results point to a clear design principle for future feature engineering:
prioritize short-horizon momentum and volatility signals over longer-horizon or
raw price features. Specifically, the Relative Strength Index (RSI) and Moving
Average Convergence Divergence (MACD) both encode short-term momentum relative
to recent price history in ways that complement rolling volatility, and could
be expected to contribute meaningfully given the dominance of the 5-day SMA
ratio in the current feature set. Bollinger Bands, which explicitly combine
moving averages with rolling standard deviation, may offer an information-
efficient alternative to including both separately. A natural next step would be
to expand the feature set to include these indicators and repeat the ablation
study to assess whether the additional signals are complementary or redundant.

\subsection{Practical Implications and Trade-offs}

While Random Forest achieves the best accuracy, its predictions are less
interpretable than Logistic Regression. In practice, financial applications may
prefer a slightly less accurate but more interpretable model for regulatory
compliance or risk management purposes. The modest accuracy gains (roughly 4--7\%
above chance for the best model) also suggest these approaches should serve as
one signal among many in a broader trading strategy, not as standalone decision
systems.

\textbf{Transaction Costs and Practical Profitability.} A key limitation not
captured by accuracy alone is the effect of transaction costs. Even a model
with 57\% accuracy can be unprofitable if it generates frequent trades, since
bid-ask spreads and commissions erode edge rapidly for daily signals. A more
practically informative evaluation would measure risk-adjusted returns (e.g.,
Sharpe ratio) under a simulated trading strategy that applies the model's
predictions with a realistic cost structure. This would directly quantify
whether the predictive edge survives market frictions.

\textbf{Confidence Calibration.} The models in this study are evaluated on
binary predictions only. In practice, the predicted probabilities output by
Logistic Regression and Random Forest can be used to size positions
proportionally to prediction confidence, rather than trading at equal size on
every signal. If well-calibrated, higher-confidence predictions could be
weighted more heavily, potentially improving risk-adjusted performance. Future
work should assess the calibration of predicted probabilities (e.g., via
reliability diagrams or Expected Calibration Error) before deploying
probability-based position sizing.

% -----------------------------------------------------------------------
\section{Limitations}
% -----------------------------------------------------------------------

\textbf{External Factors.} Financial markets are heavily influenced by
macroeconomic events, earnings surprises, and investor sentiment --- none of
which are captured in historical OHLCV data, limiting the predictive ceiling of
any model trained solely on price and volume signals.

\textbf{Non-Stationarity.} Stock market dynamics are non-stationary: statistical
properties change over time due to regime shifts and policy changes. The 2018--
2022 window includes the COVID-19 market crash and recovery (March--May 2020), a
regime shift that may inflate or deflate apparent predictability. Future work
should test models in a rolling-window or out-of-sample regime (e.g., train on
2018--2021, test on 2022) to assess whether learned patterns persist.

\textbf{Single-Asset Generalization.} Our evaluation covers only five large-cap
U.S. equities. Trained models may not generalize to small-cap stocks,
international markets, or other asset classes where dynamics differ
substantially.

\textbf{Binary Label Simplification.} Framing prediction as binary up/down
classification abstracts away price movement magnitude, which is critical for
practical trading. A 0.01\% gain and a 5\% gain are treated identically,
limiting the financial utility of predictions.

\textbf{Statistical Significance.} Performance improvements of 2--4\% across
models are relatively small. Future work should incorporate paired hypothesis
testing or bootstrapping to formally validate that observed differences are
statistically significant rather than artifacts of variance.

% -----------------------------------------------------------------------
\section{Conclusion}
% -----------------------------------------------------------------------

We presented a rigorous empirical study of classical machine learning approaches
for next-day stock price direction prediction. Our key findings are:

\begin{itemize}
    \item Random Forest achieves the strongest performance (57.2\% accuracy,
    0.573 F1), outperforming SVM and Logistic Regression baselines through its
    ability to capture non-linear feature interactions.

    \item A feature ablation study identifies the 5-day SMA ratio and rolling
    volatility as the dominant predictors, accounting for the largest drops in
    F1 when removed. Raw price and volume features contribute marginally.

    \item All models perform only modestly above the 50\% random baseline,
    providing empirical support for the semi-strong EMH on large-cap U.S.
    equities. Performance is consistent across all five stocks, ruling out
    results driven by a single favorable asset.

    \item Generalization gaps are well-controlled under regularization,
    confirming that models learn weak but genuine signal rather than memorizing
    training data.
\end{itemize}

These findings suggest that while classical ML can extract weak predictive
signals from technical indicators, practical deployment requires integration
with additional data sources (e.g., sentiment, macro indicators) and should
treat model predictions as probabilistic signals rather than deterministic
trading rules.

% -----------------------------------------------------------------------
\bibliographystyle{plainnat}
\begin{thebibliography}{9}

\bibitem[Fama(1970)]{fama1970}
Fama, E.~F. (1970).
\newblock Efficient capital markets: A review of theory and empirical work.
\newblock \emph{Journal of Finance}, 25(2), 383--417.

\bibitem[Breiman(2001)]{breiman2001}
Breiman, L. (2001).
\newblock Random forests.
\newblock \emph{Machine Learning}, 45(1), 5--32.

\bibitem[Cortes and Vapnik(1995)]{cortes1995}
Cortes, C., \& Vapnik, V. (1995).
\newblock Support-vector networks.
\newblock \emph{Machine Learning}, 20(3), 273--297.

\bibitem[Murphy(1999)]{murphy1999}
Murphy, J.~J. (1999).
\newblock \emph{Technical Analysis of the Financial Markets}.
\newblock New York Institute of Finance.

\bibitem[Fischer and Krauss(2018)]{fischer2018}
Fischer, T., \& Krauss, C. (2018).
\newblock Deep learning with long short-term memory networks for financial
market predictions.
\newblock \emph{European Journal of Operational Research}, 270(2), 654--669.

\end{thebibliography}

\appendix
\section{Supplemental Material}

\subsection{Hyperparameter Details}

All hyperparameters were fixed prior to final evaluation using preliminary
cross-validation on the training set only:

\begin{itemize}
    \item \textbf{Logistic Regression}: $C=1.0$, solver=\texttt{lbfgs},
    max\_iter=1000.
    \item \textbf{Random Forest}: 100 trees, max\_depth=10,
    min\_samples\_leaf=5, random\_state=42.
    \item \textbf{SVM}: RBF kernel, $C=1.0$, $\gamma$=\texttt{scale},
    random\_state=42.
\end{itemize}

\subsection{Dataset Statistics}

\begin{table}[ht]
\centering
\caption{Dataset statistics per stock after feature engineering warm-up period.}
\begin{tabular}{lccc}
\toprule
\textbf{Stock} & \textbf{Total Samples} & \textbf{Train} & \textbf{Test} \\
\midrule
AAPL  & 1,231 & 985  & 246 \\
MSFT  & 1,229 & 983  & 246 \\
GOOGL & 1,228 & 982  & 246 \\
AMZN  & 1,230 & 984  & 246 \\
JPM   & 1,232 & 986  & 246 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Class Balance Analysis}

A key assumption underlying the use of accuracy as a fair metric is approximate
class balance (i.e., roughly equal frequency of up and down days). Table~6
reports the fraction of positive labels ($y_t = 1$, i.e., next-day up) per
stock in both the training and test sets.

\begin{table}[ht]
\centering
\caption{Fraction of positive labels (next-day price increase) per stock.
Values close to 0.50 confirm approximate class balance, justifying accuracy
as a fair evaluation metric without the need for class-weighted corrections.}
\begin{tabular}{lcc}
\toprule
\textbf{Stock} & \textbf{Train Positive Rate} & \textbf{Test Positive Rate} \\
\midrule
AAPL  & 0.514 & 0.496 \\
MSFT  & 0.521 & 0.504 \\
GOOGL & 0.508 & 0.492 \\
AMZN  & 0.503 & 0.512 \\
JPM   & 0.517 & 0.500 \\
\midrule
\textbf{Average} & \textbf{0.513} & \textbf{0.501} \\
\bottomrule
\end{tabular}
\end{table}

All stocks exhibit near-50\% positive rates in both splits, confirming that
class imbalance is not a confound in this study. The random baseline of 50\%
accuracy is therefore a valid and tight lower bound against which model
improvements are measured.

\subsection{Feature Pairwise Correlation}

To assess potential redundancy among the eight engineered features, we compute
the Pearson correlation matrix on the training set (averaged across all five
stocks). Table~7 reports the pairwise correlations among the most correlated
feature pairs.

\begin{table}[ht]
\centering
\caption{Selected pairwise Pearson correlations between features (averaged
across 5 stocks, computed on training data only). High absolute correlations
indicate potential redundancy.}
\begin{tabular}{llc}
\toprule
\textbf{Feature A} & \textbf{Feature B} & \textbf{Avg. Correlation} \\
\midrule
5-day SMA          & 20-day SMA         & $+0.97$ \\
Price-to-SMA Ratio & 5-day SMA Ratio    & $+0.81$ \\
Daily Return       & Rolling Volatility  & $+0.43$ \\
Volume Change      & Daily Return        & $+0.18$ \\
5-day SMA Ratio    & Rolling Volatility  & $-0.12$ \\
\bottomrule
\end{tabular}
\end{table}

The near-perfect correlation between the 5-day and 20-day SMA ($r = 0.97$)
confirms that these two features are largely redundant in their raw form,
which explains their negligible individual contributions in the ablation study
(Table~\ref{tab:ablation}). The Price-to-SMA Ratio and 5-day SMA Ratio are
also highly correlated ($r = 0.81$), suggesting that future feature sets
could consolidate these into a single relative momentum indicator without
significant information loss. In contrast, the low correlation between Volume
Change and all price-based features ($|r| < 0.20$) indicates that volume
provides genuinely orthogonal information, even if its marginal contribution
to classification accuracy is small on this dataset.

% -----------------------------------------------------------------------
\newpage
\section*{NeurIPS Paper Checklist}

\begin{enumerate}

\item {\bf Claims}
    \item[] Question: Do the main claims made in the abstract and introduction accurately reflect the
paper's contributions and scope?
    \item[] Answer: \answerYes{}
    \item[] Justification: The abstract and introduction precisely state the three classifiers
    evaluated, five tickers, the 2018--2022 date range, approximate observation counts, the
    chronological split strategy, the best model and its exact metrics (57.2\% accuracy, 0.573
    F1), and the two dominant features from ablation. Every claim is directly supported by
    Tables~1--4 and the corresponding experimental sections. No aspirational result is presented
    as achieved.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the abstract and introduction do not include the claims
made in the paper.
        \item The abstract and/or introduction should clearly state the claims made, including the
contributions made in the paper and important assumptions and limitations. A [No] or
[N/A] answer to this question will not be perceived well by the reviewers.
        \item The claims made should match theoretical and experimental results, and reflect how
much the results can be expected to generalize to other settings.
        \item It is fine to include aspirational goals as motivation as long as it is clear that these goals
are not attained by the paper.
    \end{itemize}

\item {\bf Limitations}
    \item[] Question: Does the paper discuss the limitations of the work performed by the authors?
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~6 (Limitations) enumerates five explicit limitations:
    (1)~exclusion of macroeconomic and sentiment signals; (2)~non-stationarity and the
    COVID-19 regime shift within the evaluation window; (3)~generalization restricted to five
    large-cap U.S.\ equities; (4)~binary label formulation that ignores return magnitude; and
    (5)~absence of formal statistical significance testing. The Discussion additionally raises
    transaction costs and probability calibration as practical caveats.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the paper has no limitation while the answer [No] means
the paper has limitations, but those are not discussed in the paper.
        \item The authors are encouraged to create a separate ``Limitations'' section in their paper.
        \item The paper should point out any strong assumptions and how robust the results are to
violations of these assumptions (e.g., independence assumptions, noiseless settings,
model well-specification, asymptotic approximations only holding locally). The authors
should reflect on how these assumptions might be violated in practice and what the
implications would be.
        \item The authors should reflect on the scope of the claims made, e.g., if the approach was
only tested on a few datasets or with a few runs. In general, empirical results often
depend on implicit assumptions, which should be articulated.
        \item The authors should reflect on the factors that influence the performance of the approach.
For example, a facial recognition algorithm may perform poorly when image resolution
is low or images are taken in low lighting. Or a speech-to-text system might not be
used reliably to provide closed captions for online lectures because it fails to handle
technical jargon.
        \item The authors should discuss the computational efficiency of the proposed algorithms
and how they scale with dataset size.
        \item If applicable, the authors should discuss possible limitations of their approach to
address problems of privacy and fairness.
        \item While the authors might fear that complete honesty about limitations might be used by
reviewers as grounds for rejection, a worse outcome might be that reviewers discover
limitations that aren't acknowledged in the paper. The authors should use their best
judgment and recognize that individual actions in favor of transparency play an impor-
tant role in developing norms that preserve the integrity of the community. Reviewers
will be specifically instructed to not penalize honesty concerning limitations.
    \end{itemize}

\item {\bf Theory assumptions and proofs}
    \item[] Question: For each theoretical result, does the paper provide the full set of assumptions and
a complete (and correct) proof?
    \item[] Answer: \answerNA{}
    \item[] Justification: This paper is entirely empirical. It contains no theorems, lemmas, or
    formal proofs. The only mathematical content is the definition of the binary prediction
    target and the standard L2-regularized cross-entropy loss function, both of which are
    presented as implementation specifications rather than theoretical propositions requiring proof.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the paper does not include theoretical results.
        \item All the theorems, formulas, and proofs in the paper should be numbered and cross-
referenced.
        \item All assumptions should be clearly stated or referenced in the statement of any theorems.
        \item The proofs can either appear in the main paper or the supplemental material, but if
they appear in the supplemental material, the authors are encouraged to provide a short
proof sketch to provide intuition.
        \item Inversely, any informal proof provided in the core of the paper should be complemented
by formal proofs provided in appendix or supplemental material.
        \item Theorems and Lemmas that the proof relies upon should be properly referenced.
    \end{itemize}

\item {\bf Experimental result reproducibility}
    \item[] Question: Does the paper fully disclose all the information needed to reproduce the main ex-
perimental results of the paper to the extent that it affects the main claims and/or conclusions
of the paper (regardless of whether the code and data are provided or not)?
    \item[] Answer: \answerYes{}
    \item[] Justification: The paper provides: (a)~the exact data source (\texttt{yfinance} /
    Yahoo Finance, five named tickers, January 2018--December 2022); (b)~the complete
    feature engineering procedure including window sizes and formulas; (c)~all hyperparameters
    for every model (Appendix~A.1); (d)~fixed random seeds (\texttt{random\_state=42});
    (e)~the strict six-step pipeline order preventing leakage; and (f)~the full source code at
    the public GitHub repository linked in the abstract. The software stack
    (\texttt{scikit-learn}~v1.3, Python~3.10) is also specified.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the paper does not include experiments.
        \item If the paper includes experiments, a [No] answer to this question will not be perceived
well by the reviewers: Making the paper reproducible is important, regardless of
whether the code and data are provided or not.
        \item If the contribution is a dataset and/or model, the authors should describe the steps taken
to make their results reproducible or verifiable.
        \item Depending on the contribution, reproducibility can be accomplished in various ways.
For example, if the contribution is a novel architecture, describing the architecture fully
might suffice, or if the contribution is a specific model and empirical evaluation, it may
be necessary to either make it possible for others to replicate the model with the same
dataset, or provide access to the model. In general. releasing code and data is often
one good way to accomplish this, but reproducibility can also be provided via detailed
instructions for how to replicate the results, access to a hosted model (e.g., in the case
of a large language model), releasing of a model checkpoint, or other means that are
appropriate to the research performed.
        \item While NeurIPS does not require releasing code, the conference does require all submis-
sions to provide some reasonable avenue for reproducibility, which may depend on the
nature of the contribution. For example
        \begin{itemize}
            \item[(a)] If the contribution is primarily a new algorithm, the paper should make it clear how
to reproduce that algorithm.
            \item[(b)] If the contribution is primarily a new model architecture, the paper should describe
the architecture clearly and fully.
            \item[(c)] If the contribution is a new model (e.g., a large language model), then there should
either be a way to access this model for reproducing the results or a way to reproduce
the model (e.g., with an open-source dataset or instructions for how to construct
the dataset).
            \item[(d)] We recognize that reproducibility may be tricky in some cases, in which case
authors are welcome to describe the particular way they provide for reproducibility.
In the case of closed-source models, it may be that access to the model is limited in
some way (e.g., to registered users), but it should be possible for other researchers
to have some path to reproducing or verifying the results.
        \end{itemize}
    \end{itemize}

\item {\bf Open access to data and code}
    \item[] Question: Does the paper provide open access to the data and code, with sufficient instruc-
tions to faithfully reproduce the main experimental results, as described in supplemental
material?
    \item[] Answer: \answerYes{}
    \item[] Justification: The full source code is publicly available at
    \url{https://github.com/allbertkim/Final-Project.git}, as stated in the abstract. The
    dataset is automatically fetched at runtime via the \texttt{yfinance} library from Yahoo
    Finance (a freely accessible public API), so no private or licensed data is involved. Any
    reader can reproduce the dataset by running the provided code with the same tickers and
    date range.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that paper does not include experiments requiring code.
        \item Please see the NeurIPS code and data submission guidelines (\url{https://neurips.cc/
public/guides/CodeSubmissionPolicy}) for more details.
        \item While we encourage the release of code and data, we understand that this might not
be possible, so [No] is an acceptable answer. Papers cannot be rejected simply for not
including code, unless this is central to the contribution (e.g., for a new open-source
benchmark).
        \item The instructions should contain the exact command and environment needed to run to
reproduce the results. See the NeurIPS code and data submission guidelines (\url{https:
//neurips.cc/public/guides/CodeSubmissionPolicy}) for more details.
        \item The authors should provide instructions on data access and preparation, including how
to access the raw data, preprocessed data, intermediate data, and generated data, etc.
        \item The authors should provide scripts to reproduce all experimental results for the new
proposed method and baselines. If only a subset of experiments are reproducible, they
should state which ones are omitted from the script and why.
        \item At submission time, to preserve anonymity, the authors should release anonymized
versions (if applicable).
        \item Providing as much information as possible in supplemental material (appended to the
paper) is recommended, but including URLs to data and code is permitted.
    \end{itemize}

\item {\bf Experimental setting/details}
    \item[] Question: Does the paper specify all the training and test details (e.g., data splits, hyperpa-
rameters, how they were chosen, type of optimizer) necessary to understand the results?
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~3.5 (Reproducibility) and Section~4.1 (Experimental Setup)
    jointly specify: the chronological 80/20 split and its rationale, all hyperparameter values
    and the selection method (domain knowledge and preliminary cross-validation on training
    data only), loss functions for each model, the absence of a separate validation set, library
    versions (\texttt{scikit-learn} v1.3), and hardware. Appendix~A.1 provides a dedicated
    hyperparameter table and Appendix~A.2 lists per-stock dataset statistics.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the paper does not include experiments.
        \item The experimental setting should be presented in the core of the paper to a level of detail
that is necessary to appreciate the results and make sense of them.
        \item The full details can be provided either with the code, in appendix, or as supplemental
material.
    \end{itemize}

\item {\bf Experiment statistical significance}
    \item[] Question: Does the paper report error bars suitably and correctly defined or other appropriate
information about the statistical significance of the experiments?
    \item[] Answer: \answerNo{}
    \item[] Justification: The paper reports point estimates (accuracy, precision, recall, F1)
    averaged across five stocks but does not include standard deviations, confidence intervals,
    or hypothesis tests. The Limitations section explicitly acknowledges this gap and recommends
    paired testing or bootstrapping as future work. Per-stock results in Table~4 provide a partial
    substitute by demonstrating consistency of the signal across all five assets.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the paper does not include experiments.
        \item The authors should answer [Yes] if the results are accompanied by error bars, confidence
intervals, or statistical significance tests, at least for the experiments that support the
main claims of the paper.
        \item The factors of variability that the error bars are capturing should be clearly stated (for
example, train/test split, initialization, random drawing of some parameter, or overall
run with given experimental conditions).
        \item The method for calculating the error bars should be explained (closed form formula,
call to a library function, bootstrap, etc.)
        \item The assumptions made should be given (e.g., Normally distributed errors).
        \item It should be clear whether the error bar is the standard deviation or the standard error
of the mean.
        \item It is OK to report 1-sigma error bars, but one should state it. The authors should
preferably report a 2-sigma error bar than state that they have a 96\% CI, if the hypothesis
of Normality of errors is not verified.
        \item For asymmetric distributions, the authors should be careful not to show in tables or
figures symmetric error bars that would yield results that are out of range (e.g., negative
error rates).
        \item If error bars are reported in tables or plots, the authors should explain in the text how
they were calculated and reference the corresponding figures or tables in the text.
    \end{itemize}

\item {\bf Experiments compute resources}
    \item[] Question: For each experiment, does the paper provide sufficient information on the com-
puter resources (type of compute workers, memory, time of execution) needed to reproduce
the experiments?
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~4.1 (Experimental Setup) specifies the hardware (Intel Core
    i7 CPU, 16~GB RAM), operating system and software environment (Python~3.10,
    \texttt{scikit-learn}~v1.3), and total training time (under 5 minutes across all models and
    stocks). No GPU or cloud compute is required; all experiments run on a standard personal
    computer, making reproduction broadly accessible.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the paper does not include experiments.
        \item The paper should indicate the type of compute workers CPU or GPU, internal cluster,
or cloud provider, including relevant memory and storage.
        \item The paper should provide the amount of compute required for each of the individual
experimental runs as well as estimate the total compute.
        \item The paper should disclose whether the full research project required more compute
than the experiments reported in the paper (e.g., preliminary or failed experiments that
didn't make it into the paper).
    \end{itemize}

\item {\bf Code of ethics}
    \item[] Question: Does the research conducted in the paper conform, in every respect, with the
NeurIPS Code of Ethics \url{https://neurips.cc/public/EthicsGuidelines}?
    \item[] Answer: \answerYes{}
    \item[] Justification: The research uses only publicly available historical financial market data,
    involves no human subjects or sensitive data, poses no direct harms, and releases code
    openly. The Discussion explicitly cautions against treating model outputs as standalone
    trading decisions, reducing risk of harmful deployment. No aspect of the work conflicts
    with the NeurIPS Code of Ethics.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the authors have not reviewed the NeurIPS Code of
Ethics.
        \item If the authors answer [No], they should explain the special circumstances that require a
deviation from the Code of Ethics.
        \item The authors should make sure to preserve anonymity (e.g., if there is a special consid-
eration due to laws or regulations in their jurisdiction).
    \end{itemize}

\item {\bf Broader impacts}
    \item[] Question: Does the paper discuss both potential positive societal impacts and negative
societal impacts of the work performed?
    \item[] Answer: \answerYes{}
    \item[] Justification: The Discussion (Section~5.3) addresses both sides. Positive impacts
    include providing a reproducible benchmark for financial ML research and offering an
    empirical check on the semi-strong EMH. Negative impacts are also noted: the paper warns
    that modest predictive accuracy (57\%) can be harmful if misapplied in automated trading
    systems without accounting for transaction costs or model uncertainty, and explicitly advises
    treating predictions as probabilistic signals within broader strategies rather than standalone
    rules.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that there is no societal impact of the work performed.
        \item If the authors answer [N/A] or [No], they should explain why their work has no societal
impact or why the paper does not address societal impact.
        \item Examples of negative societal impacts include potential malicious or unintended uses
(e.g., disinformation, generating fake profiles, surveillance), fairness considerations
(e.g., deployment of technologies that could make decisions that unfairly impact specific
groups), privacy considerations, and security considerations.
        \item The conference expects that many papers will be foundational research and not tied
to particular applications, let alone deployments. However, if there is a direct path to
any negative applications, the authors should point it out. For example, it is legitimate
to point out that an improvement in the quality of generative models could be used to
generate Deepfakes for disinformation. On the other hand, it is not needed to point out
that a generic algorithm for optimizing neural networks could enable people to train
models that generate Deepfakes faster.
        \item The authors should consider possible harms that could arise when the technology is
being used as intended and functioning correctly, harms that could arise when the
technology is being used as intended but gives incorrect results, and harms following
from (intentional or unintentional) misuse of the technology.
        \item If there are negative societal impacts, the authors could also discuss possible mitigation
strategies (e.g., gated release of models, providing defenses in addition to attacks,
mechanisms for monitoring misuse, mechanisms to monitor how a system learns from
feedback over time, improving the efficiency and accessibility of ML).
    \end{itemize}

\item {\bf Safeguards}
    \item[] Question: Does the paper describe safeguards that have been put in place for responsible
release of data or models that have a high risk for misuse (e.g., pre-trained language models,
image generators, or scraped datasets)?
    \item[] Answer: \answerNA{}
    \item[] Justification: The paper poses no high-risk misuse concerns. No pre-trained model,
    image generator, or scraped dataset is released. The publicly released asset is a
    \texttt{scikit-learn}-based pipeline using freely available market data. The Discussion
    explicitly frames the models as research tools requiring integration with broader strategies
    rather than autonomous trading systems.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the paper poses no such risks.
        \item Released models that have a high risk for misuse or dual-use should be released with
necessary safeguards to allow for controlled use of the model, for example by requiring
that users adhere to usage guidelines or restrictions to access the model or implementing
safety filters.
        \item Datasets that have been scraped from the Internet could pose safety risks. The authors
should describe how they avoided releasing unsafe images.
        \item We recognize that providing effective safeguards is challenging, and many papers do
not require this, but we encourage authors to take this into account and make a best
faith effort.
    \end{itemize}

\item {\bf Licenses for existing assets}
    \item[] Question: Are the creators or original owners of assets (e.g., code, data, models), used in
the paper, properly credited and are the license and terms of use explicitly mentioned and
properly respected?
    \item[] Answer: \answerYes{}
    \item[] Justification: The paper cites \texttt{scikit-learn} (BSD-3 license), \texttt{yfinance}
    (Apache 2.0 license), and \texttt{pandas} (BSD license) as software dependencies. Yahoo
    Finance data is accessed via a public API consistent with its terms of service for research
    and educational use. All academic works used are properly cited in the bibliography with
    full references.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the paper does not use existing assets.
        \item The authors should cite the original paper that produced the code package or dataset.
        \item The authors should state which version of the asset is used and, if possible, include a
URL.
        \item The name of the license (e.g., CC-BY 4.0) should be included for each asset.
        \item For scraped data from a particular source (e.g., website), the copyright and terms of
service of that source should be provided.
        \item If assets are released, the license, copyright information, and terms of use in the
package should be provided. For popular datasets, \url{paperswithcode.com/datasets}
has curated licenses for some datasets. Their licensing guide can help determine the
license of a dataset.
        \item For existing datasets that are re-packaged, both the original license and the license of
the derived asset (if it has changed) should be provided.
        \item If this information is not available online, the authors are encouraged to reach out to
the asset's creators.
    \end{itemize}

\item {\bf New assets}
    \item[] Question: Are new assets introduced in the paper well documented and is the documentation
provided alongside the assets?
    \item[] Answer: \answerYes{}
    \item[] Justification: The primary new asset is the publicly released code repository at
    \url{https://github.com/allbertkim/Final-Project.git}, which implements the full
    pipeline described in the paper. A video walkthrough is also linked in the abstract. The
    paper itself constitutes documentation of the pipeline, hyperparameters, and experimental
    protocol. No novel datasets or pretrained models are released; data is fetched dynamically
    via \texttt{yfinance}.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the paper does not release new assets.
        \item Researchers should communicate the details of the dataset/code/model as part of their
submissions via structured templates. This includes details about training, license,
limitations, etc.
        \item The paper should discuss whether and how consent was obtained from people whose
asset is used.
        \item At submission time, remember to anonymize your assets (if applicable). You can either
create an anonymized URL or include an anonymized zip file.
    \end{itemize}

\item {\bf Crowdsourcing and research with human subjects}
    \item[] Question: For crowdsourcing experiments and research with human subjects, does the paper
include the full text of instructions given to participants and screenshots, if applicable, as
well as details about compensation (if any)?
    \item[] Answer: \answerNA{}
    \item[] Justification: This paper involves no crowdsourcing, no human participants, and no
    annotation tasks. All data is publicly available historical market data.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the paper does not involve crowdsourcing nor research
with human subjects.
        \item Including this information in the supplemental material is fine, but if the main contribu-
tion of the paper involves human subjects, then as much detail as possible should be
included in the main paper.
        \item According to the NeurIPS Code of Ethics, workers involved in data collection, curation,
or other labor should be paid at least the minimum wage in the country of the data
collector.
    \end{itemize}

\item {\bf Institutional review board (IRB) approvals or equivalent for research with human
subjects}
    \item[] Question: Does the paper describe potential risks incurred by study participants, whether
such risks were disclosed to the subjects, and whether Institutional Review Board (IRB)
approvals (or an equivalent approval/review based on the requirements of your country or
institution) were obtained?
    \item[] Answer: \answerNA{}
    \item[] Justification: No human subjects are involved. The study uses publicly available
    historical financial market data and requires no IRB review or equivalent approval.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the paper does not involve crowdsourcing nor research
with human subjects.
        \item Depending on the country in which research is conducted, IRB approval (or equivalent)
may be required for any human subjects research. If you obtained IRB approval, you
should clearly state this in the paper.
        \item We recognize that the procedures for this may vary significantly between institutions
and locations, and we expect authors to adhere to the NeurIPS Code of Ethics and the
guidelines for their institution.
        \item For initial submissions, do not include any information that would break anonymity (if
applicable), such as the institution conducting the review.
    \end{itemize}

\item {\bf Declaration of LLM usage}
    \item[] Question: Does the paper describe the usage of LLMs if it is an important, original, or
non-standard component of the core methods in this research? Note that if the LLM is used
only for writing, editing, or formatting purposes and does not impact the core methodology,
scientific rigor, or originality of the research, declaration is not required.
    \item[] Answer: \answerNA{}
    \item[] Justification: LLMs are not used as any component of the core methods. The
    classifiers evaluated are Logistic Regression, Random Forest, and SVM --- all classical
    statistical learning methods. Any use of LLMs was limited to writing assistance and does
    not impact the methodology, experimental results, or scientific conclusions.
    \item[] Guidelines:
    \begin{itemize}
        \item The answer [N/A] means that the core method development in this research does not
involve LLMs as any important, original, or non-standard components.
        \item Please refer to our LLM policy in the NeurIPS handbook for what should or should not
be described.
    \end{itemize}

\end{enumerate}

\end{document}
